---
title: "Notes on simulating return volumes"
output: html_notebook
---

To understand risk from returning NZers under various scenarios, we need:

 - Estimate of NZers returning from each country under the current regime (quarantine for returning NZ residents)
 - Estimate of the NZers who would return from each country under a looser regime (e.g., short quarantines or business as usual)
 - To expose overall risk when simulating opening a country to a looser regime, we need to
    - Subtract the NZers currently returning from that country
    - Add the NZers who would return under the looser regime, considered at the normal prevalence level for that country.

```{r}
nz_res_arrivals <- readr::read_csv("data/stats-nz-infoshare-nz-NZ-resident traveller arrivals by EVERY country of main destination and purpose (Monthly)_formatted.csv")
colnames(nz_res_arrivals)[1]<-"Date"
```



## Estimate of NZers returning from each country under the current regime (quarantine for returning NZ residents)

Most returnees are from Australia (Megan Woods at Government Press Conference, 24 July 2020, Radio NZ).

I've filed an OIA to get this data. In the meantime, Stats NZ Infoshare's series "NZ-resident traveller arrivals by EVERY country of main destination and purpose (Monthly)” contains data for May 2020 that we can use.

```{r}

```


## Estimate of the NZers who would return from each country under a looser regime (e.g., short quarantines or business as usual)

We can use "NZ-resident traveller arrivals by EVERY country of main destination and purpose (Monthly)”.

```{r}
res_arrivals_may_2020 <-nz_res_arrivals %>% filter(Date=="2020M05") %>% select(-Date) %>% t %>% data.frame

colnames(res_arrivals_may_2020)[1]<-"ArrivalCount"
res_arrivals_may_2020%>% arrange(desc(ArrivalCount))
```

## Issues

Some people may be considered both "non-resident" and "resident" and hence be double-counted.

For instance, New Zealand citizens who are resident in Australia may be counted as "non resident" (and hence be included in the non-resident arrivals by country of residence) and "NZ resident" (by default, because they are NZ citizens; hence they are included in our NZ resident monthly arrivals count).


