---
title: "Country Profile"
output:
  pdf_document: default
#  html_document: default
params:
  location_profile: NA
  trust_rating: NA
  location_info: NA
  nz_info: NA
  country_classification: NA
  assumed_ifr: NA
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

country_classification_names <- function(country_classification){
  if (country_classification==2){
    return("safe")
  }else if (country_classification==3){
    return("low to moderate risk")
  }else if(country_classification==4){
    return("high risk")
  }else{
    return("unknown risk")
  }
}
options(scipen=10)
```

```{r setup2, include=FALSE}


locname <- params$location_profile

lifeExp <- params$location_info$LifeExp

if(params$location_info$LifeExp>=70){
  health_system_description<-"trustworthy"
  lifeExpDescription = "high"
}else{
  health_system_description<-"not trustworthy"
  lifeExpDescription = "low"
}



```

# `r locname`

This is a location profile for `r locname`.

## Internal risk

```{r}
scale_signif <- function(x,figures=2){
  if(x<1){
    return(as.character(signif(x,figures)))
  }else{
    return(as.character(scales::comma(signif(x,figures))))
  }
}
```


### COVID-19 prevalence



`r locname` currently has `r scale_signif(params$location_info$ActiveCases)` official active confirmed cases. 

Two weeks ago, `r locname` had `r scale_signif(params$location_info$LaggedNewCases*7,2)` new cases over a seven day period. Over the last week, there have been `r signif(params$location_info$NewDeaths*7)` new deaths. This is a case fatality rate of `r signif(params$location_info$NewDeaths/params$location_info$LaggedNewCases*100,2)`%. Based on international research ([Russell et al., 2020](https://www.eurosurveillance.org/docserver/fulltext/eurosurveillance/25/12/eurosurv-25-12-3.pdf?expires=1595971685&id=id&accname=guest&checksum=D0BDDC4636765D23E28F7C144F813284)) we assume the actual infection-fatality rate, including undetected infections, is actually `r params$assumed_ifr*100`%, so we estimate that `r locname` is officially detecting `r signif(params$location_info$InferredDetectionRate*100,2)`% of their cases. That means the true number of active infections is likely around `r signif(1/params$location_info$InferredDetectionRate,2)` times the number of confirmed cases. Considering this detection rate, and the current number of official active confirmed cases over the last week (around `r scale_signif(params$location_info$ActiveCases,2)`), we estimate the true number of infections currently in `r locname` is closer to `r scale_signif(params$location_info$InferredActiveCases)`.

Prevalence of COVID-19 in `r locname` is therefore estimated at `r scale_signif(params$location_info$InfActiveCasesPerMillion,3)` active infections per million, in a population of `r scale_signif(params$location_info$Population/10^6,2)` million. Compare this to the current New Zealand case rate of `r signif(params$nz_info$InfActiveCasesPerMillion,2) ` active infections per million. 
<!--This is the "inferred" infection rate. It accounts for the likely number of undetected cases by starting with the detected case rate, and adjusting upward depending on the number of fatalities in the relevant country.-->

### Quality of health data reporting

Health data reporting in `r locname` has a trust rating of **`r params$trust_rating`**. This is because its health system is considered `r health_system_description ` due to `r locname`'s `r lifeExpDescription` life expectancy of `r round(lifeExp,0)`.

Our estimates are robust to under-reported cases of COVID-19; however, our estimate does assume that the number of _deaths_ reported due to COVID-19 in `r locname` is not under-reported (whereas an over-estimate of deaths could lead to an over-estimate of the risk). For this reason it is important that we can trust health data reporting in `r locname`.

## Travel to New Zealand

This month last year, New Zealand received `r scale_signif(params$location_info$LocationResidentMonthlyArrivalsWeighted) ` arrivals who were _resident_ in `r locname`. This includes citizens of that country residing there, and citizens of New Zealand and other countries who reside in `r locname`. Over the same time there were also `r scale_signif(params$location_info$NZResidentMonthlyArrivalsWeighted) ` New Zealand residents returning to New Zealand whose main destination while away was `r locname`. By adding these figures together we can roughly estimate the number of people who arrive in New Zealand per month after being in `r locname` in the previous 14 days at `r scale_signif(params$location_info$TotalExpectedMonthlyArrivals) `.

New Zealand citizens and residents are always permitted to return home to New Zealand from `r locname`. Very few return while there is a mandatory quarantine in place, but we expect that greater numbers will return from there if quarantine restrictions were to be loosened.

## Expected risk


We consider the case rate of COVID-19 in `r locname`, 
the likely true number of infections, the monthly number of arrivals from 
`r locname`, and the country's trust rating to identify an overall expected risk.

```{r echo=FALSE}

if(params$trust_rating=="trustworthy"){
  risk_statement <- paste0(
      "Due to these considerations we expect, if the border were completely open to ",
      locname,
      ", the expected number of cases arriving from ",
      locname,
      " would be ",
      as.character(signif(params$location_info$ExpectedNumberOfCasesAll,2)),
      " every month. <br />\n",
      "If the border were open, with all travelers from ",locname, " screened before entry, the expected case numbers exposed to the community would be reduced to ",
      as.character(signif(params$location_info$ExpectedNumberOfCasesEscapingOneScreen,2)),". ",
      "If two independent tests were run before releasing travelers, this could be reduced to ",
      as.character(signif(params$location_info$ExpectedNumberOfCasesEscapingTwoScreens,2)),
      ".\n<br /><br /> A 14 day quarantine provides even lower risk. Considering New Zealand's quarantine system as it has existed over the last few months, a quarantine system could ensure that only around ",
      as.character(signif(params$location_info$ExpectedNumberOfCasesInCommunity,2)),
      " cases would be exposed to the community. Actual cases under quarantine would be lower still due to the suppression of travel in response to a quarantine system.")
}else
{
  risk_statement <- (
    paste0("Due to the trust rating for health data reporting in ",
           locname, ", rated ", params$trust_rating,
           " an overall expected risk cannot be calculated.",
           " On that basis it is assumed that ", locname, " is a high-risk location."
           )
  )
}

```

These figures do NOT take into account the reduction in travel likely to result from the implementation of border control measures such as quarantine.

`r risk_statement`


## Overall rating: `r country_classification_names(params$country_classification)`

The overall rating for `r locname` is `r country_classification_names(params$country_classification)`.





