---
title: "Country Profile"
output:
  pdf_document: default
#  html_document: default
params:
  location_profile: NA
  data_date: NA
  trust_rating: NA
  location_info: NA
  nz_info: NA
  assumed_ifr: NA
  level_thresholds: NA
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

country_classification_names <- function(country_classification){
  if (country_classification==2){
    return("Level 2")
  }else if (country_classification==3){
    return("Level 3")
  }else if(country_classification==4){
    return("Level 4")
  }else{
    return("unknown risk")
  }
}
options(scipen=10)
```

```{r setup2, include=FALSE}


locname <- params$location_profile

lifeExp <- params$location_info$LifeExp

if(params$location_info$LifeExp>=70){
  health_system_description<-"trustworthy"
  lifeExpDescription = "high"
}else{
  health_system_description<-"not trustworthy"
  lifeExpDescription = "low"
}



```

# `r locname`

This is a location profile for `r locname` as of `r as.character(params$data_date,format="%d %B %Y")`.

## Internal risk

```{r}
scale_signif <- function(x,figures=2){
  if(x<1){
    return(as.character(signif(x,figures)))
  }else{
    return(as.character(scales::comma(signif(x,figures))))
  }
}

scale_dp <- function(x,dp=0){
    if(x<1){
    return(as.character(round(x,dp)))
  }else{
    return(as.character(scales::comma(round(x,dp))))
  }
}
```


### COVID-19 prevalence



`r locname` currently has `r scale_dp(params$location_info$ActiveCases)` official active confirmed cases. 

Three weeks ago, `r locname` had `r scale_dp(params$location_info$LaggedNewCases*7,2)` new cases over a seven day period (some of these may be imported cases in managed isolation/quarantine, MIQ). Over the last week, there have been `r signif(params$location_info$NewDeaths*7)` new deaths. This is a case fatality rate of `r signif(params$location_info$NewDeaths/params$location_info$LaggedNewCases*100,2)`%. Based on international research ([Russell et al., 2020](https://www.eurosurveillance.org/docserver/fulltext/eurosurveillance/25/12/eurosurv-25-12-3.pdf)) we assume the actual infection-fatality rate, including undetected infections, is actually `r params$assumed_ifr*100`%, so we estimate that `r locname` is officially detecting `r signif(100/params$location_info$InferredDetectionRate,2)`% of their cases. That means the true number of active infections could be up to `r signif(params$location_info$InferredDetectionRate,2)` times the number of confirmed cases. Considering this detection rate, and the current number of active confirmed cases (around `r scale_dp(params$location_info$ActiveCases,2)`), we estimate the true number of infections currently in `r locname` is closer to `r scale_dp(params$location_info$InferredActiveCases)`.

Prevalence of COVID-19 in `r locname` is therefore estimated at `r scale_signif(params$location_info$InfActiveCasesPerMillion,3)` active infections per million, in a population of `r scale_signif(params$location_info$Population/10^6,3)` million. Compare this to the current New Zealand case rate of `r signif(params$nz_info$InfActiveCasesPerMillion,3) ` active infections per million. In low prevalence locations, these two may not be strictly comparable because MIQ cases have not been removed from the New Zealand data.
<!--This is the "inferred" infection rate. It accounts for the likely number of undetected cases by starting with the detected case rate, and adjusting upward depending on the number of fatalities in the relevant country.-->

### Quality of health data reporting

Health data reporting in `r locname` has a trust rating of **`r params$trust_rating`**. This is because its health system is considered `r health_system_description ` due to `r locname`'s `r lifeExpDescription` life expectancy of `r round(lifeExp,0)`. A life expectancy of less than 70 indicates a lower quality of healthcare, and could indicate problems with health data recording, including reporting of fatality rates. For this reason, we do not advise relying on Covid-19 reporting in countries with a life expectancy under 70 without careful verification.

Our estimates are robust to under-reported cases of COVID-19; however, our estimate does assume that the number of _deaths_ reported due to COVID-19 in `r locname` is not under-reported (whereas an over-estimate of deaths could lead to an over-estimate of the risk). For this reason it is important that we can trust health data reporting in `r locname`.

## Travel to New Zealand

This month last year, New Zealand received `r scale_dp(params$location_info$LocationResidentMonthlyArrivalsScaled1) ` arrivals who were _resident_ in `r locname`. This includes citizens of that country residing there, and citizens of New Zealand and other countries who reside in `r locname`. Over the same time there were also `r scale_dp(params$location_info$NZResMonthlyArrivalsScaled1) ` New Zealand residents returning to New Zealand whose main destination while away was `r locname`. By adding these figures together we can roughly estimate the number of people who arrived in New Zealand per month in 2019 after being in `r locname` in the previous 14 days at `r scale_dp(params$location_info$Total2019MonthlyArrivals) `. This is an approximation of the travel volume we are most interested in: the number of people coming to New Zealand who were present in `r locname` in the last 14 days.

New Zealand citizens and residents are always permitted to return home to New Zealand from `r locname`. Very few return while there is a mandatory quarantine in place, but we expect that greater numbers will return from there if quarantine restrictions were to be loosened.

Based on the intervention applied, we have estimated that in the Proposed Intervention, `r scale_dp(params$location_info$MonthlyArrivalsWeighted)` travellers could arrive in New Zealand each month from `r locname`. This compares to an estimated `r scale_dp(params$location_info$StatusQuoMonthlyArrivals)` now.





## Expected risk


We consider the case rate of COVID-19 in `r locname`, 
the likely true number of infections, the monthly number of arrivals from 
`r locname`, and the country's trust rating to identify an overall expected risk.

```{r echo=FALSE}

if(params$trust_rating=="trustworthy"){
  risk_statement <- paste0(
      "Due to these considerations we expect, if the border were completely open to ",
      locname,
      ", the expected number of cases entering the traveller journey from ",
      locname,
      " would be ",
      scale_signif(params$location_info$ExpectedCasesAtBorderAt2019Levels,3),
      " every month")
  
  if(params$location_info$ExpectedCasesAtBorderAt2019Levels<0.5){
      risk_statement <- paste0(
      risk_statement, " (one every ", round(1/params$location_info$ExpectedCasesAtBorderAt2019Levels), " months)"
      )
    }
      
  risk_statement <- paste0(risk_statement,
      ". <br />\n")
  if (params$location_info$InterventionLabel!="None"){
    risk_statement <- paste0(
      risk_statement,
      "If travelers from ",locname, " go through an intervention, ",params$location_info$InterventionLabel,
      #".\n<br /><br /> A 14 day quarantine provides even lower risk. Considering New Zealand's quarantine system as it has existed over the last few months, a quarantine system could ensure that only around ",
        ", then only around ",
      scale_signif(params$location_info$ExpectedNumberOfCasesInCommunity,3),
      " cases would exit MIQ into the community")
    if(params$location_info$ExpectedNumberOfCasesInCommunity<0.5){
      risk_statement <- paste0(
      risk_statement, " (one every ", round(1/params$location_info$ExpectedNumberOfCasesInCommunity), " months)"
      )
    }
    
    risk_statement <- paste0(
      risk_statement,
    ". Actual cases under quarantine would be lower still due to the suppression of travel in response to a quarantine system.")
  }

            
}else
{
  risk_statement <- (
    paste0("Due to the trust rating for health data reporting in ",
           locname, ", rated ", params$trust_rating,
           " an overall expected risk cannot be calculated.",
           " On that basis it is assumed that ", locname, " is a high-risk location."
           )
  )
}

```

These figures do _not_ take into account the reduction in travel likely to result from the implementation of border control measures such as quarantine.

`r risk_statement`




## Overall rating: `r params$location_info$PrevalenceRating`


<!--

level_1_max <- input$intsim_level1_max_prevalence
    level_2_max <- input$intsim_level2_max_prevalence
    level_3_max <- input$intsim_level3_max_prevalence
-->
Our risk categories are "COVID-free" (0 active infections), "Level 1" (0 to `r params$level_thresholds$level_1_max` per 100k), "Level 2" (`r params$level_thresholds$level_1_max` to `r params$level_thresholds$level_2_max` per 100k), "Level 3" (`r params$level_thresholds$level_2_max` to `r params$level_thresholds$level_3_max` per 100k), and "Level 4" (more than `r params$level_thresholds$level_3_max` per 100k). For Level 4 countries, we propose continuing existing restrictions and adding a pre-departure PCR test. For all others, from COVID-free to Level 3 locations, some level of non-residents could be allowed in without excessive risk.

Due to the current active case prevalence in `r locname` of `r scale_signif(params$location_info$InfActiveCasesPerMillion/10,3)` per 100k, the overall rating for `r locname` is `r params$location_info$PrevalenceRating`.


