---
title: "Get manual risk matrix report"
output: html_notebook
---

```{r setup, include=FALSE}
# require("knitr")
# knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = "app/")
# getwd()
# setwd("app/")
```

This notebook is for manually generating a risk matrix report.

```{r}

library(DT)
source("../app/utils.R")
source("../app/simulation.R")
source("../app/country_classification_rules.R")
library(ggrepel)

run_date<-as.Date("2020-08-22")#Sys.Date()
source("../app/defaults.R")

#Ben J:
#Assume 0.5% transmission risk without mask (it’s a conservative worst case rate)
#If mask use reduces risk by 90% as per Arthur’s email then in-flight transmission risk reduced to 0.05%
#Therefore one case expected to be acquired ‘in-flight’ for every 125 infectious cases carried
default_aircraft_infection_rate <- 0.005 #without mask
default_aircraft_mask_effectiveness_percent <- 90



month_name <- format(run_date,"%B")



setwd("../app")

```


```{r}
nogeo_world_basic_data <- 
  get_geomapped_covid_data(life_exp_thresh,run_date,separate_aussie_states_and_hk = TRUE,include_geo_data = FALSE)
```


```{r}

geo_world_with_covid_data <- simulate_treatment_for_countries(nogeo_world_basic_data,
                                                    treatment_effectiveness = default_assumed_effectiveness,
                                                    extra_spread = 0,
                                                     assumed_ifr = default_assumed_ifr_percent/100,
                                                     
                                                     traveler_relative_prevalence=default_traveler_relative_prevalence,
                                                     current_lockdown_passenger_volume = default_current_lockdown_passenger_volume
                                                     )
```




```{r}
source("key_interest_countries.R")
#prettify the column names
covid_data_to_save<-
geo_world_with_covid_data %>% 
  filter(Location %in% key_interest_countries) %>%
  arrange(LocationCode) %>%
  mutate(
    InfActiveCasesPerMillion = round(InfActiveCasesPerMillion,1),
    PredictedActiveCasesPerMillion = round(PredictedActiveCasesPerMillion,1),
    PredictedActiveCases = round(PredictedActiveCases,0),
    
  ) %>% 
  select(
    #location info
    `Location Code` = `LocationCode`,
    `Location` = `Location`,
    `Population` = `Population`,
    
    
    
    #assessing expected cases
    `Total Confirmed Cases` = `CasesConfirmed`,
    `Total Fatalities` = `Deaths`,
    `Total Recoveries` = `Recoveries`,
    `Active Cases` = `ActiveCases`,
    PredictedActiveCases = PredictedActiveCases,
    #health data trust
    `Life Expectancy` = `LifeExp`,
    
    #assessing expected prevalence
    `Mean daily fatalities in last 7 days` = `NewDeaths`,
    `Mean daily cases in last 7 days of two weeks prior`=LaggedActiveCases,
    `Infection detection ratio` = `InferredDetectionRate`,
    `Estimated active infections` = `InferredActiveCases`,
    `Estimated Prevalence (per million)` = `InfActiveCasesPerMillion`,
    
    #assess any recent increase in cases,
    `Estimated Predicted Prevalence (per million)` = PredictedInfActiveCasesPerMillion,
    
    
    #risk to new zealand
    #`Monthly arrivals of residents from location to NZ in 2019` = `LocationResidentMonthlyArrivals`,
    #`Monthly arrivals of returning NZ residents from location in 2019` = `NZResMonthlyArrivals`,
    
    `Expected monthly arrivals` = `MonthlyArrivalsWeighted`,
    `Expected monthly arrivals with active infection` = `ExpectedCasesAtBorder`,
    #`Expected monthly arrivals with active infection passing screening` = `ExpectedNumberOfCasesEscapingOneScreen`,
    `Expected monthly active cases leaking from quarantine` = `ExpectedNumberOfCasesInCommunity`
  )
  

```



```{r}
library(ggplot2)
source("key_interest_countries.R")
#we need traveller prevalence and expected volume


current_risk_per_thousand<-sum(geo_world_with_covid_data$ExpectedCasesAtBorderUnderLockdown,na.rm=TRUE)/sum(geo_world_with_covid_data$MonthlyArrivalsLockdownScaled2,na.rm=TRUE)*1000

#we draw an area plot that needs coordinates
#ordered by InferredActiveCaseTravelerRate from lowest to highest
#coloured by PrevalenceRating
#each country needs two data points in our area plot - the start and the end of it.
#and we need a cumulative graph
relevant_data <- geo_world_with_covid_data %>% 
  filter(Location %in% key_interest_countries) %>%
  arrange(InferredActiveCaseTravelerRate) %>%
  select(Location,MonthlyArrivalsWeighted,InferredActiveCaseTravelerRate,PrevalenceRating) %>%
  mutate(CumulativeTravelExclusive=cumsum(MonthlyArrivalsWeighted)-MonthlyArrivalsWeighted,
         CumulativeTravelInclusive=cumsum(MonthlyArrivalsWeighted)
         )
  
  
start_points <- relevant_data %>% 
  mutate(
    TravelCumulative=CumulativeTravelExclusive)

end_points <- relevant_data %>% 
  mutate(
    TravelCumulative=CumulativeTravelInclusive)

all_points_line <- rbind(start_points,end_points) %>% arrange(InferredActiveCaseTravelerRate,TravelCumulative)


```

```{r}

all_rects <-
  relevant_data %>% 
  mutate(CasesPerThousand=InferredActiveCaseTravelerRate*10^3) %>%
  mutate(bottom=0,
         RectLabel=Location,
         top=CasesPerThousand,
         left=CumulativeTravelExclusive,
         right=CumulativeTravelInclusive,
         label_xpos=CumulativeTravelExclusive + MonthlyArrivalsWeighted/2,
         label_ypos=0)

all_rects <- all_rects %>%
  mutate(RectId=1:nrow(all_rects)#,
         #GroupId=as.numeric(NA)
         )
```
  
```{r}
  
#all_rects[1,"GroupId"]=1
for (rect_i in 2:nrow(all_rects)){
  #now for each row, set the rectgroup to the minimum rectID where the row label_xpos has less than a certain difference.
  current_rectID<-all_rects[[rect_i,"RectId"]]
  current_xpos <- all_rects[[rect_i,"label_xpos"]]
  group_base_rect_candidates <- all_rects %>% filter(label_xpos > (current_xpos - 15000) & RectId<current_rectID)
  if(nrow(group_base_rect_candidates)>0){
    group_base_rect<-group_base_rect_candidates[1,]
    #print(paste0(group_base_rect$Location, " taking ", all_rects[[rect_i,"Location"]]))
    group_base_rect_id <- group_base_rect$RectId
      #and move the xpos back to reflect the change.
    all_rects[[rect_i,"label_xpos"]] <- group_base_rect[["label_xpos"]]
    #now merge the labels
    #print(group_base_rect_id)
    all_rects <- all_rects %>% 
      mutate(RectLabel=ifelse(RectId==group_base_rect_id,
                              paste0(RectLabel,"\n",all_rects[[rect_i,"RectLabel"]]),
                              RectLabel
                              ))

    all_rects[[rect_i,"RectLabel"]] = ""
  }

  
}

34/9000*1000

```


```{r}
library(RColorBrewer)
level_rects <- all_rects %>% 
  filter(PrevalenceRating!="Unknown") %>%
  group_by(PrevalenceRating) %>% 
  summarise(
    left = min(CumulativeTravelExclusive),
    right = max(CumulativeTravelInclusive),
    top=max(all_rects$CasesPerThousand)*2,
    bottom=-max(all_rects$CasesPerThousand),
    max_prevalence=max(InferredActiveCaseTravelerRate)
    ) %>% 
  arrange(max_prevalence)
  
level_rects$LevelColour=brewer.pal(n = nrow(level_rects), name = "Blues")
```


```{r}

  
  
#ggplot(all_points,aes(x=TravelCumulative,y=InferredActiveCaseTravelerRate))+geom_line()
ggplot(all_rects,aes(xmin=left, xmax=right, ymin=bottom,ymax=top))+
  #draw the levels
  geom_rect(data=level_rects,mapping=aes(xmin=left, xmax=right, ymin=bottom,ymax=top,fill=PrevalenceRating),
            alpha=0.5,
            fill=brewer.pal(n = nrow(level_rects), name = "Blues"))+
  geom_text_repel(data=level_rects,mapping=aes(left, label=PrevalenceRating),segment.color = "transparent",
            y=max(all_rects$CasesPerThousand)*2/3,
            hjust=1,
            size=3,
            color="black",
            fill=brewer.pal(n = nrow(level_rects), name = "Blues"))+
  #draw the countries
  geom_vline(aes(xintercept=CumulativeTravelInclusive),linetype="dotted",color="#aaaaaa")+
  geom_rect(color="#9999ff",fill="#000055",alpha=0.8)+
  geom_text(aes(label_xpos,y=label_ypos,label=RectLabel),
                  angle=30,size=3,hjust=1,vjust=1)+
  #draw the current average prevalence
  geom_hline(yintercept = current_risk_per_thousand,color="#cc0000")+
  geom_text(x=0,y=current_risk_per_thousand,vjust=0,hjust=0,color="#cc0000",label="Status quo aggregate traveller risk\n",size=3)+
  #set the scales and style
  scale_x_continuous(name="Cumulative expected travellers per month", labels=scales::comma_format(),)+
  scale_y_continuous(name="Cases per 1,000 travellers",breaks = c(0,2,4,6,8,10,12),minor_breaks = NULL)+
  coord_cartesian(ylim=c(-max(all_rects$CasesPerThousand)/4,max(all_rects$CasesPerThousand)))+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())+
  labs(title="Risk prior to applying any interventions")
  
  


```


## progressive graph

this is a line graph that shows the cumulative number of cases and passengers added as we add countries from the least risky to the most.

Would this be fundamentally the same as our previous graph?

It's a bit different: we show cumulative cases per month against cumulative traveller volume per month.

Probably quite simple to render - we need a table where each row includes a label and a cumulative count...




```{r}

geo_world_with_covid_data <- simulate_treatment_for_countries(nogeo_world_basic_data,
                                                    treatment_effectiveness = default_assumed_effectiveness,
                                                    extra_spread = 0,
                                                     assumed_ifr = default_assumed_ifr_percent/100,
                                                     travel_volume_proportion=0.2,
                                                     traveler_relative_prevalence=default_traveler_relative_prevalence,
                                                    current_lockdown_passenger_volume=default_current_lockdown_passenger_volume
                                                     )
covid_data<-geo_world_with_covid_data
```

```{r}
covid_data <- 
    covid_data %>% 
  filter(!is.na(ExpectedNumberOfCasesInCommunity) & !is.na(MonthlyArrivalsWeighted)) %>%
    mutate(InterventionApplied =
             if_else(
               (PrevalenceRating %in% c("COVID-free","Low","Moderate","High") &
                 Location %in% key_interest_countries)
               ,TRUE,FALSE)
    )
  
cumulative_intervention_graph <- covid_data %>% 
  arrange(InterventionApplied,InferredActiveCaseTravelerRate) %>%
  select(Location,ExpectedNumberOfCasesInCommunity,MonthlyArrivalsWeighted,
         PrevalenceRating,InferredActiveCaseTravelerRate,
         InterventionApplied
  ) %>%
  mutate(CumulativeExpectedCases=cumsum(ExpectedNumberOfCasesInCommunity),
         CumulativeExpectedTravellers=cumsum(MonthlyArrivalsWeighted),
         PointLabel=if_else(InterventionApplied,Location,as.character(NA)),
         Scenario="Intervention"
  ) %>%
  select(-ExpectedNumberOfCasesInCommunity,-MonthlyArrivalsWeighted)
  

#we might want to add the status quo....
status_quo_cumulative_graph <- covid_data %>%
  arrange(InferredActiveCaseTravelerRate) %>%
  select(Location,ExpectedNumberOfCasesInCommunityUnderLockdown,StatusQuoMonthlyArrivals,
           PrevalenceRating,InferredActiveCaseTravelerRate
    ) %>%
    mutate(CumulativeExpectedCases=cumsum(ExpectedNumberOfCasesInCommunityUnderLockdown),
           CumulativeExpectedTravellers=cumsum(StatusQuoMonthlyArrivals),
           PointLabel=as.character(NA),
           Scenario="StatusQuo",
           InterventionApplied=FALSE
           ) %>%
  select(-ExpectedNumberOfCasesInCommunityUnderLockdown,-StatusQuoMonthlyArrivals)

cumulative_graph <- rbind(cumulative_intervention_graph,status_quo_cumulative_graph)
  
```



```{r}
status_quo_risk <-max((cumulative_graph %>% filter(Scenario=="StatusQuo"))$CumulativeExpectedCases)
ggplot(cumulative_graph,
       aes(x=CumulativeExpectedTravellers,y=CumulativeExpectedCases,label=PointLabel,color=interaction(InterventionApplied,Scenario),group=Scenario))+
  geom_line()+geom_point()+geom_label_repel(size=2)+
  scale_color_manual(values=c("green","black","red"))+
  scale_x_continuous(name="Cumulative expected travellers per month", labels=scales::comma_format())+
  geom_hline(yintercept = status_quo_risk,color="#cc0000")+
  geom_text(x=0,y=status_quo_risk,vjust=0,hjust=0,color="#cc0000",label="Status quo aggregate traveller risk\n",size=3)+

  guides(color="none")+
  scale_y_continuous(
  #scale_y_log10(
    name="Cumulative expected cases per Month",
                labels=function(x){as.character(x)},
                minor_breaks = NULL)+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

